---
title: "Parallel"
format: pdf
editor: visual
---
# Question 1

```{r}
#| echo: true
#| message: false
#| warning: false

#install.packages("doParallel")

library(doParallel)

library(kableExtra)

library(tibble)

library(dplyr)

#Creating threads 
c1 = makeCluster(4)

#Assigning threads
registerDoParallel(c1)

cat("Serial time")
#Serial
system.time({
  result = foreach(i = 1:100, .combine = "rbind") %do% {
    s = rexp(100, 1)
    resultrow = c(mean(s), var(s))
  }
})

#Parallel
cat("Parallel time")
system.time({
  result = foreach(i = 1:100, .combine = "rbind") %dopar% {
    s = rexp(100, 1)
    resultrow = c(mean(s), var(s))
  }
})


tibbleResults = as.data.frame(result) |> rename(Mean = V1, Variance = V2)
head(tibbleResults)
```


# Question 2

```{r}
#| message: false
#| warning: false
library(MASS)
gal <- galaxies

B = 1000

bs = matrix(0,ncol = length(gal),nrow = B)

#Serial 
system.time({
  result = foreach(i = 1:B, .combine = "rbind") %do% {
    s = sample(gal,82,T)
    median(s)
  }
})


#Creating threads 
c1 = makeCluster(4)

#Assigning threads
registerDoParallel(c1)

#Parallel but very slow
system.time({
  result = foreach(i = 1:B, .combine = "c") %dopar% {
    s = sample(gal,82,T)
    median(s)
  }
})

#Dividing work into threads 
work_size = 1000 #Amount of work given to each thread
n_threads = B / work_size


system.time({
  result = foreach(i = 1:n_threads, .combine = "c",packages = "MASS") %dopar% {
    replicate(work_size, median(sample(gal, 82, TRUE)))
  }
  })

stopCluster(c1)
```

For small number of samples the serial solution is faster (values of B below 300) but soon after parallel solution begins to perform significantly better. For 1000 samples there is 3.875x speed up which is close to the theoretical maximum of 4 for 4 threads.

# Question 3

```{r}

#Number of times interval contains 1 
count = 0

#Number of times loop runs
total = 100

#Serial
timeSerial = system.time({
  for(i in 1:total) {
        B = 1000
        #Drawing sample from exponential distribution 
        s = rexp(50,1)
        
        #Generate bootstrap sample 
        bs = matrix(0,ncol = 50,nrow = B)
        
        for(i in 1:B) {
          samp = sample(s,50,T)
          
          bs[i,] = samp
        }
        
        bsMeans = apply(bs,1,mean)
        
        c1 = quantile(bsMeans,0.025,names = F)
        
        c2 = quantile(bsMeans, 0.975,names = F)
        
        
        x = ifelse(c1 <= 1 & c2 >= 1,1,0)
        
        count = count + x
}
  
})


timeSerial

coverage = (count/total)*100
coverage

#Parallel implementation

#Creating threads 
c1 = makeCluster(4)

#Assigning threads
registerDoParallel(c1)

timeParallel= system.time({
  

    count2 = foreach(1:total,.combine =c) %dopar% {
      
       #Drawing sample from exponential distribution 
       s = rexp(50,1)
       
       #Bootstrap 
       bsMeans2 = replicate(1000,mean(sample(s,50,T)))
       
       #Computing quantiles 
       c1 = quantile(bsMeans2,0.025,names = F)
       c2 = quantile(bsMeans2, 0.975,names = F)
       
       #Assigning value to count 
       ifelse(c1 <= 1 & c2 >= 1,1,0)
    }
    
})

timeParallel

#Percentage
sum(count2)

stopCluster(c1)
```
The coverage for both the serial and the parallel implementations are both values in the low 90s which is below the expected 95% but not by a significant amount 

# Question 4

```{r}
set.seed(1234)

#Crate a random vector of 5 values 3 times and in each loop find the maximum of that random vector 
result = foreach(x = irnorm(5, count = 3), .combine = c) %do% {
  max(x)
}

result
```

# Question 5

## ParApply 

```{r}
#| echo: false
#| message: false
#| warning: false

size = 10000

#Threads 
cP = makeCluster(4)

registerDoParallel(cP)

set.seed(1234)

v1 = rnorm(size,0,1)

v2 = rnorm(size,0,1)

v3 = rnorm(size,0,1)


#Making a matrix of vectors 
m1 = cbind(v1,v2,v3)

#
ParApplyTime = system.time({result = parApply(cP,m1,2,max)})


stopCluster(cP)

ParApplyTime
```

## Replicate 

```{r}
replicateTime = system.time({replicate(3,max(rnorm(size,0,1)))})
replicateTime
```

## foreach 

```{r}


foreachTime = system.time({result = foreach(x = irnorm(size, count = 3), .combine = c) %do% {
  max(x)
} })

foreachTime
```

There is no meaningful difference between the running times but the serial replicate is faster than both foreach and parApply
